\documentclass{my_cv}
\usepackage{multicol}
\usepackage{tabularx} % in the preamble
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=40mm,
 }


\begin{document}
\name{Sean Borg}
\contactInfo
{23 keats ave, Rochdale, Lancs, Ol127PZ}
{07492 308 491}
{01706 868 974}
{sean@seanborg.tech}
{www.seanborg.tech}


\section{Employment}

\workDetails
{Open Data Manchester}
{software developer}
{Contract}
{Manchester, United Kingdom}
{May 2019 - July 2019}
\workdetails
{Made 3D printed map of greater Manchester visualising the May 2019 local elections }
{Modelled and printed Lego base plates in the shape of the UK}
{Skills obtained: Knowledge of  OpenScad, creating STL models}
\stopworkdetails

\workDetails
{Handsfree group}
{software developer}
{Contract} %should i call it consultancy
{Manchester, United Kingdom}
{January 2018 - Current}
\workdetails
{Created the front end for an internal audit app for DPD, in Angular (JavaScript). Along with updating and maintaining the back end }
{Full stack created an earned recognition app using Django (Python) for the back end and Angular (JavaScript) for the front end.}
{Fixes and improvements to a telematics system both front (Angular) and back end (Django).}
{Skills obtained: Knowledge of  Angular, Django and Google cloud platform}
\stopworkdetails

\section{Work Experience}
\workDetails
{Late Rooms}
{Data Science}
{Full Time}
{Manchester, United Kingdom}
{1 week August 2017}

\workdetails
{Helped build pipeline for a neural network}
{Writing SQL queries for future analytics}
{Skills obtained: use of git in industry, using kanban model to distribute work around a team}
\stopworkdetails
%Helped build a pipeline for a neural network and writing SQL queries for future analytics. Learnt how git is used in industry, and how to use the kanban model to distribute work around a team.  

\section{Education}
\educationDetails
{Bangor University}
{Bangor,Gwynedd, United Kingdom}
{September 2015 - June 2018}

Achieved  2:1

\workdetails
{Above 80\% in Java, C and Databases}
{Technologies used: Github, slack and Object oriented design}
\stopworkdetails

\educationDetails
{Holy Cross College}
{Bury, Lancashire, United Kingdom }
{September 2012 - June 2014}


A-Level results;\\
\begin{tabularx}{\textwidth}{X l X l} 
Computing A-level & (C) &  Maths A-level & (B) \cr
Further Maths A-level & (B) & Physics AS & (B) \cr 
\end{tabularx}


\educationDetails
{Oulder Hill Community School}
{Rochdale, Lancashire, United Kingdom}
{September 2007 - May 2012}



GCSE results;\\
\begin{tabularx}{\textwidth}{X l X l} 
English language & (C) & Mathematics & (A*) \cr
Graphics &  (B) & Biology & (A) \cr 
Chemistry & (A) & Physics & (A) \cr
Further mathematics qualification & (B) & Resistance materials & (B)
\end{tabularx}

\section{Personal projects}
\subsection{\textbf {Visual Algorithms \hfill Android app}}
%\workdetails
Small app created to learn more about java and android programming.\\
Source code at www.github.com/seam345/VisualAlgorthms
%\stopworkdetails
\subsection{\textbf {AI competition \hfill Programming competition}}
%\workdetails
65th out of 2405, creating a program to play Reversi(Othello).\\
www.hackerearth.com/challenge/competitive/battle-of-bots-5/
%\stopworkdetails

\subsection{\textbf {\LaTeX \hfill Self taught}}

Learned how to use LaTeX for this CV,  then later used  it for my dissertation.


\subsection{\textbf {Git \hfill Self taught}}

Read through git pro book to better understand Git, a tool I now use every day.


\section{Other employment}

\workDetails
{Scandinave spa}
{Night cleaner}
{Part time 32 hours pw}
{Whistler, B.C., Canada}
{April 2015 -- July 2015}
 
\workdetails
{ Nightly clean (12am-8am) of the entire spa including; Steam room, Hot tubs, Massage pavilion.}
{Skills obtained: Presentable organising of furniture and separating work in a team. }
\stopworkdetails



\workDetails
{Whistler Vacation club}
{General helper}
{As needed up to 40 hours pw}
{Whistler, B.C., Canada}
{March 2015 -- July 2015}

\workdetails
{Initially clearing water damaged rooms.}
{Later on keeping all public area of the hotel clean and tidy.}
{Skills obtained: Good time management, working in a ever changing environment.}
\stopworkdetails



\workDetails
{Whistler Blackcomb}
{Vallay cleaner}
{Full time 40 hours per week}
{Whistler, B.C., Canada}
{September 2014 -- March 2015}

\workdetails
{Daily cleaning of Whistler Blackcomb's 3 main restaurant bars (G.L.C., Dustys, Merlins) as well as routine maintenance of the grounds and the public toilets.}
{During the down season I also full cleaned most of their buildings on the Whistler and Blackcomb Mountain.}
{Skills obtained: Self motivation and Keeping to a tight time schedule}
\stopworkdetails

%Daily cleaning of Whistler Blackcomb's 3 main restaurant bars (G.L.C., Dustys, Merlins) as well as routine maintenance of the grounds and the public toilets. During the down season I also full cleaned most of their buildings on the Whistler and Blackcomb Mountain.

%
%\workDetails
%{PC World (Dixons Retail)}
%{Knowhow adviser}
%{Part time 20 hours per week}
%{Rochdale, Lancashire, United Kingdom}
%{September 2013 -- May 2014}
%
%\workdetails
%{Set up and repair old and new computers, laptops, tablet etc.}
%{Dealing with any returns and general customer services.}
%{Skills obtained: Customer service, working a till}
%\stopworkdetails

%Knowhow staff set up and repair old and new computers, laptops, tablet etc. as well as dealing with any returns and general customer services.

%\workDetails
%{Pete Spence}
%{Farm hand and Landscape labourer }
%{Part time}
%{Rochdale, Lancashire, United Kingdom}
%{August 2012 - September 2013}
%
%\workdetails
%{Initially painting round the entire farm.}
%{Progressed to help with their logging business (www.lucyslogs.co.uk).}
%{Further help with general tasks on the farm including additional help with his landscaping business (www.pnslandscapes.co.uk)}
%{Skills obtained: Keeping punctual,  Awareness of health and safety procedures.}
%\stopworkdetails

%Initially painting round the entire farm, progressing to help with their logging business (www.lucyslogs.co.uk). Further help with general tasks on the farm including additional help with his landscaping business (www.pnslandscapes.co.uk). Still currently doing the odd job such as leaflet designing and formatting for mail shot and sales campaign











\end{document} 


